---
title: "Example code"
output: 
  html_notebook: 
    toc: yes
---

```{r setup, echo=FALSE}
library(tidyverse)
library(REDCapR)
```

--------------------------------------------------------------------------------

## Downloading data from REDCap using `REDCapR`

Submit your REDCap query:

```{r redcap_read_ex1}
query <- REDCapR::redcap_read(
  redcap_uri = 'https://redcap.vanderbilt.edu/api/',
  token = Sys.getenv('REDCAP_API_KEY_VU')
)
```

This returns a list with various pieces of information:

```{r}
names(query)
```

You care about `data`, which has the dataframe with the info you want. So, we do

```{r}
my_data <- query$data
# View first few rows...
head(my_data)
```
You can do more sophisticated queries. **This is especially useful in larger datasets because it saves time in downloading.** For example, you can request a 
subset of your data by:

- Tiempoint / event (e.g., visit 1, visit 2)
- Form / instrument (e.g., phq9, gad7)
- Specific fields (e.g., phq9_totalscore, gad7_totalscore)

For example, here I only download the patient initials, phq9 total, and gad7
total:

```{r redcap_read_ex2}
query <- REDCapR::redcap_read(
  redcap_uri = 'https://redcap.vanderbilt.edu/api/',
  token = Sys.getenv('REDCAP_API_KEY_VU'),
  fields = c('pt_initials', 'phq9_total_score','sc_tot_score')
)

result <- query$data
head(result)
```

### Building queries for your shiny apps: practical advice 

- In small datasets, you could get away with downloading all the data once, and then filtering/transforming the data within the app as the client changes inputs/outputs

- In larger datasets, you might need to make multiple, focused queries (especially if the datasets have lots of variables!)
