---
title: "From simple to complex"
output: html_notebook
---

```{r setup}
library(tidyverse)
library(plotly)
```

Consider the clinical dashboard. We can break down the tasks into:

1. Get latest patient questionnaire data into R from REDCap
2. Clean data
3. Wrangle data to prepare it for my plot
4. Make the plot
5. (Optional): make plot nicer with `ggplotly`
6. Convert into dashboard

## Step 1: read data from REDCap

```{r step01_get_data_from_redcap}
my_data <- REDCapR::redcap_read(
  redcap_uri = Sys.getenv('REDCAP_API_URL_VU'),
  token = Sys.getenv('REDCAP_API_KEY_VU_SUPERFAKE')
)$data %>% tibble()

head(my_data)
```

## Step 2: clean data.

Naturalistic data has weird stuff (e.g., patients with initials like fM, or who put dots between them). We want to clean it to make sure it works for our plots.

```{r step02_clean_data}
clean_data <- my_data %>%
    filter(preappt_survey_complete == 2) %>% # so we dont get unfinished ones
    mutate(pt_initials = pt_initials %>% # clean out initials
             toupper() %>% # capitalize (in case of, e.g. Fm or fM)
             str_replace_all('\\.','') # remove dots (if they do F.M.)
           ) 
```

## Step 3: wrangle data.

To get our data ready for making a plot, we want to subset only a specific patient's stuff, and pivot it from wide to long format. We do that here.

```{r step03_wrangle_data}
patient_selected <- 'CC'

# subset data to include only stuff for this patient
filtered_data <- clean_data %>% 
  filter(pt_initials == patient_selected) %>% # only keep patient_selected's data
  select(pt_initials, date_time, phq9_total_score, sc_tot_score) %>% # keep only relevant vars
  drop_na() %>% # remove incomplete rows
  pivot_longer(cols = c('phq9_total_score','sc_tot_score'), # pivot from wide to long
                     names_to = 'scale',
                     values_to = 'total_score')
```

## Step 4: make plot

```{r step04_make_plot}
# make the plot using ggplot arguments
plt <- filtered_data %>% 
  ggplot(aes(x=date_time, y=total_score, color=scale)) +
  geom_line() +
  geom_point() +
  ylim(0,23) + # based on PHQ-9 limits
  geom_hline(yintercept=10, linetype='dotted') +
  labs(x='Date', y='Score', 
       color = 'Scale',
       title='Self-report scale scores') +
  theme(legend.position = 'top') +
  scale_colour_brewer(palette = "Set1")

plt
```

## Step 5: make plot nicer using ggplotly
```{r step05_make_plot_nicer}
ggplotly(plt)
```

## Step 6: convert into dashboard

Check out `shiny_app_examples/clinical_dashboard_01_simple.R` for a shiny-fied version of this code.